A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-07 papers/gabb17/gabb17-pollard.tex
Added ideal curve to bfs_ss, expanded abstract.
Added some more citations and cleaned up R code.

\begin{document}
\maketitle
\begin{abstract}
In this paper we analyze the performance of four parallel graph processing systems to determine their performance and scalability using synthetic and real-world datasets. We perform analysis for three algorithms: breadth first serach, single source shortest paths, and PageRank. This paper examines previously overlooked aspects of parallel programming performance such as file I/O in addition to a more detailed performance analysis.
\end{abstract}

@@

@@

>>>>

\begin{document}
\maketitle
\begin{abstract}
There are an intimidating number of parallel graph processing systems. One survey in 2014 identified over 80. Since then, the landscape has changed; some packages have become inactive, even more projects have been introducted, and the previous top performers are being usurped. To address the high churn of projects and the complexity of selecting a system for a given problem, we analyze the performance and scalability of four parallel open source graph processing systems (GraphMat, GAP Benchmark Suite, GraphBIG, and PowerGraph) using synthetic and real-world datasets. We perform analysis for three algorithms: breadth first search, single source shortest paths, and PageRank. We compare our results to largest parallel graph processing performance and benchmarking project: Graphalytics. This paper examines previously overlooked aspects of parallel graph processing performance such as energy usage in addition to a detailed performance analysis modeled after the Graph500 that takes into consideration multiple runs and the phases of computation that graph programs typically undergo.
\end{abstract}

@@

The complexity of Graphalytics obfuscates the true behavior of the algorithm. We use GraphMat, the single source shortest paths algorithm, the dota-league dataset, and the default settings as an example here. By default, Graphalytics generates an HTML report giving the runtimes for each dataset in seconds. Two separate runs for a single dataset, all else being equal, gave 5.6 seconds. However, perusing the log files reveals a more complete picture: of these 5.6 seconds, 0.19 was spent computing the shortest paths while the remaining time consisted of building the necessary data structures.

@@

We use the Performance Application Programming Interface (PAPI) \cite{Browne:2000:PAPI} to gain access to Intel's Running Average Power Limit (RAPL), which provides access to a set of hardware counters measuring energy usage.
